---
title: "Logistic Regression"
output: github_document
author: "Anders Poirel"
date: 06-23-2019
---

*More practice in R, especially learning how to do stuff in the tidyverse.*

```{r, message = FALSE}
library(tidyverse)
```

we want to build a model predicting whether a customer opened a promotional email
Read the data:

```{r, message = FALSE}
data <- read_csv("P12-Email-Offer.csv")
```
We have a sample of a 100 customers, and for each of them  age, gender and whether they opned the email
```{r}
print(data)
```

This is a classification problem in with only two possible categories - the customer opens the email (1) or doesn't (0). A logistic regression model may thus be appropriate for this problem:

```{r}
lr_model <- glm(TookAction ~ Age + Gender, data = data, family = binomial)
summary(lr_model)
```

We use the fitted model to find the predicted values for the original dataset. To obtain 0-1 values instead of probabilities, we predict 1 for probabilities >= 0.5 and 0 otherwise.

```{r}
preds <- predict(lr_model, type = "response")
preds <- if_else(preds >= 0.5, 1, 0)
```

Use these predictions to compute the number of true positives and negatives, and of false positive and negatives:
```{r}
t_pos <- sum(if_else(data$TookAction == 1 & preds == 1, 1, 0))
t_neg <- sum(if_else(data$TookAction == 0 & preds == 0, 1, 0))
f_pos <- sum(if_else(data$TookAction == 0 & preds == 1, 1, 0))
f_neg <- sum(if_else(data$TookAction == 1 & preds == 0, 1, 0))
```


We can now visualize the model's predictions as follows:
```{r}
coeffs <- c(t_neg, f_neg, f_pos, t_pos) 
tr <- c(0, 1, 0, 1) # values used to build confusion matrix
pr <- c(0, 0, 1, 1) 

confusion_m <- ggplot(mapping = aes(x = tr, y = pr, fill = coeffs)) + 
  geom_tile() +
  geom_text(mapping = aes(label = coeffs), color = "white") +
  guides(fill = F) +
  coord_equal() +
  labs(title = "Confusion matrix", x = "true", y = "predicted") +
  scale_x_continuous(breaks = c(0,1)) +
  scale_y_continuous(breaks = c(0,1)) +
  theme_minimal()
  
confusion_m
```



